---
sstitle: "Final Project:Christina, Gaia Menni, Alex Palache"
output:
  prettydoc::html_pretty:
    theme: architect
date: "2024-03-14"
---

```{r, include = FALSE}
library(tidyverse)
library(data.world)
library(ggrepel)
library(prettydoc)
library(kableExtra)

```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
dataset1 <- data.world ::query(data.world::qry_sql("SELECT * FROM lovoo_v3_users_api_results"), dataset = "https://data.world/jfreex/dating-app-user-profiles-stats-lovoo-v3")

```
# FINAL PROJECT

## Backround Information 

According to Pew Research Center up to 53% of couples under 30 met online. The proliferation of dating apps has transformed the landscape of modern romance, providing individuals with unprecedented opportunities to connect with potential partners. Amidst the array of features offered by these platforms, the option to pay for enhanced profile visibility, known as "highlighting," has emerged as a strategy to increase user engagement. Profile highlighting aims to elevate the visibility of user profiles within the app's interface, potentially amplifying opportunities for interaction and connection. ^[Bouke de Vries 2023 <https://doi.org/10.1007/s10676-023-09704-y>]We want to examine  

## Hypothesis
The research question at hand is whether users who opt for profile highlighting receive more likes and profile visits compared to those who do not utilize this feature.

Alternitavly we want to look at what the best strategy at finding love is




## Describe the Dataset

This data was collected in the Spring of 2015 (April - May). The dating app used to get this data is called Lovoo, an app primarily used in European countries. The data was gotten from the profiles of the users involved. The people involved in this study were chosen by Lovoo's algorithm. Units of observations include numerical values (ex:Age), M/F for gender, individual profile names, and True/False in place of Yes/No. 


## Transformations
### How did we make the data set tidy (include code chunk)
```{r}
#THIS NEEDS WORK
```

### What variables did we create
```{r}
str(dataset1)
dataset <-dataset1 %>%
  mutate(total_interaction = counts_kisses + counts_profilevisits + counts_fans)%>%
  select(isvip, verified, ishighlighted, total_interaction, counts_kisses, counts_profilevisits, counts_fans)

view(dataset)


```

### How did you transform the dataset to visualize it? INCLUDE 2 EX
```{r}
#I want to combine these three things into one table by themselves and arrange in descending order 
interaction_data <- merge(dataset1, highlighted_interaction, by = NULL)
#DO WE STILL NEED THIS?
View(interaction_data)
  
```

### Exploration (include 2-3 exploratory vizualisations)
```{r}
dataset1 %>%
  mutate(total_interaction = counts_kisses + counts_profilevisits) %>%
  ggplot() +
  geom_jitter(aes(x = ishighlighted, y = total_interaction))


dataset1 %>%
  mutate(total_interaction = counts_kisses + counts_profilevisits) %>%
  filter(total_interaction != "173713") %>%
  ggplot() +
  geom_jitter(aes(x = ishighlighted, y = total_interaction))
 

dataset %>%
  filter(total_interaction != "173713") %>%
  mutate(subgroup = interaction(isvip, verified, ishighlighted),
         fill_variable = factor(case_when(
           isvip == TRUE ~ "isvip",
           verified == TRUE ~ "verified",
           ishighlighted == TRUE ~ "ishighlighted",
           isvip == FALSE ~ "isvip",
           verified == FALSE ~ "verified",
           ishighlighted == FALSE ~ "ishighlighted"
         ), levels = c("isvip", "verified", "ishighlighted"))) %>%
  ggplot() + 
  geom_boxplot(aes(x = subgroup, y = total_interaction, fill = fill_variable)) +
  labs(title = "Figure 1", x = "Subgroup", y = "Total Interaction", fill = "Variables") +
  scale_fill_manual(values = c("isvip" = "blue", "verified" = "green", "ishighlighted" = "pink")) +
  theme_minimal() +
  theme(axis.text.x = element_blank()) +
  coord_cartesian(ylim = c(0, 9000))



```

## Findings and Interpretations
create result table
result viz include code chunk for this
```{r}
#ishighlighted final boxplot
dataset1 %>%
  mutate(total_interaction = counts_kisses + counts_profilevisits) %>% 
  filter(total_interaction != "173713") %>% 
  ggplot(aes(x = ishighlighted, y = total_interaction)) +
  geom_jitter(color = "red") +
  geom_boxplot(outlier.shape = NA, alpha = 0.05) +
  ylim(0,40000)


#verified final boxplot
dataset1 %>%
  mutate(total_interaction = counts_kisses + counts_profilevisits+counts_fans) %>% 
  filter(total_interaction != "173713") %>% 
  ggplot(aes(x = verified, y = total_interaction)) +
  geom_jitter(color = "green") +
  geom_boxplot(outlier.shape = NA, alpha = 0.05) +
  ylim(0,40000)

#isvip final boxplot
dataset1 %>%
  mutate(total_interaction = counts_kisses + counts_profilevisits + counts_fans) %>% 
  filter(total_interaction != "173713") %>% 
  ggplot(aes(x = isvip, y = total_interaction)) +
  geom_jitter(color = "blue") + 
  geom_boxplot(outlier.shape = NA, alpha = 0.05) +
  ylim(0,40000)


```

## Conclusion (answer following questions)
What do your findings reveal about the relationship of interest?
How might you refine your hypothesis?
What significance does figuring out this relationship hold for society/science at large? (we’re likely tackling small problems here, so don’t be intimidated by this big language, it’s always important to explain why figuring out what you’re figuring out is *somehow* worth caring about. Stating the significance is always your pre-emptive answer to someone’s “so what?” question)

LOTS OF CONCLUSION STATEMENTS. WOOOO. WORDS. WORDS. WORDS. WORDS. WORDS. WORDS. SIGNIFICANCE. WOOO. One drawback to this dataset is that it ends after the participants went on a first date. Data on the longevity of the relationship, if the participants on the first date entered a relationship together, would provide more insite onto the effectiveness of the app in pairing people together. Considering that dating apps are a primary source of introduction between people looking for relationships the effectiveness of an app, Lovoo or any dating app, would be important information to know, out of interest and for the general public when they choose what app they download. 


