---
sstitle: "Final Project:Christina, Gaia, Alex"
output: html_document
date: "2024-02-29"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
dataset1 <- read.csv("https://query.data.world/s/7gnr3abaibjhwswennwfmct3pwbcre?dws=00000", header=TRUE, stringsAsFactors=FALSE);
```

##Backround Information 

The proliferation of dating apps has transformed the landscape of modern romance, providing individuals with unprecedented opportunities to connect with potential partners. Amidst the array of features offered by these platforms, the option to pay for enhanced profile visibility, known as "highlighting," has emerged as a strategy to increase user engagement. Profile highlighting aims to elevate the visibility of user profiles within the app's interface, potentially amplifying opportunities for interaction and connection. ^[Bouke de Vries 2023 <https://doi.org/10.1007/s10676-023-09704-y>] The research question at hand is whether users who opt for profile highlighting receive more likes and profile visits compared to those who do not utilize this feature.

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
